\documentclass{article}

\usepackage{hyperref}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}

\title{Progress Notes 1}
\author{Alexandra Steiner}

\begin{document}
\maketitle

The \href{text referenced}{https://www.reddit.com/r/transgendercirclejerk/comments/ec8ici/i\_had\_a\_conversation\_with\_a\_transgendered\_about/} for this report is a short piece taken from the subreddit r/transgendercirclejerk. \linebreak{}

Honestly, I was fairly hesitant to use this content for this report since I know that the subjects touched upon are very touchy today. However, given this work is one that I find extraordinarily funny, I decided to use it. This piece is a satirization of some of the worst arguments for the non-existence of transgender people. The characterization of the author is meant to be from the perspective of a poster on the subreddit r/AITA (Am I The A**hole), and is depicted as a typical (I don't know how else to describe it) Shapiro-ish troll. In the text, the author describes an comment argument between themselves and a trans woman and asks the audience for affirmation, fully expecting to receive it. From the way the author is written, 

The post makes use of a number of tropes. The way r/AITA commonly mishandles posts about transgender topics. The prevalence of Shaprioist trolls and their typical methods for arguing against transgender rights. However, this work mostly centers around how most anti-trans theories are based on unfalsifiable claims. For example, modern "gender critical" rhetoric argues that trans people are not happier after transition and those that report that they are lied on the survey. This exact argument is reflected in the text.

This work relies on an \emph{extremely} specialized experience: People who have experience arguing with “Shaprio”ish people online about trans issues, experience with the AITA subreddit in regards to trans issues, and a familiarity with arguments from a gender critical point of view



\end{document}